---
title: "Exploration"
output: html_document
---
The purpose of this markown file is to update and create a lot of the datasets in the environment in r studio to be used in the other files. (is relevant for mcda, density, and random forests).
```{r setup, include=FALSE}


library(rgeos)
library(rgdal)
library(leaflet)
library(magrittr)
library(raster)
library(spatstat)
library(sf)
library(ggplot2)
library(ggmap)
library(dplyr)
library(maptools)
library(proj4)
library(ggrepel)
library(data.table)
library(tidyverse)
library(lubridate)
library(RColorBrewer)
library(classInt)
library(maps)
library(gdistance)
library(distances)
library(geosphere)
library(spdplyr)
```




```{r}
#this file contains all of the tract centroids
tract_cent<-readOGR(dsn="SJV/tract_centroid.sqlite", layer="tract_centroid")

env_2<-readOGR(dsn="SJV/env_2.sqlite", layer="env_2")

#transmission lines
trans_lines<-readOGR(dsn="SJV/trans_lines.sqlite", layer="trans_lines")

gas_lines<-readOGR(dsn="SJV/gaslines.sqlite", layer="gaslines")

#agriculture
agr<-readOGR(dsn="SJV/cal_ag.sqlite", layer="cal_ag")

agr_sf<-as(agr, "sf")

#summarizing acres of agriculture
agr_sf2<-agr_sf%>%group_by(tract)%>%summarize(ag_area = sum(acres))

#adding agricultural area to the environmental data
env_sf<-as(env_2, "sf")
env_sf%>%st_join(agr_sf2,by=c("tract"))


#here we can make the tract_comb file from the env_stat later in QGIS. saving the file as a spatial frame and then you can convert it into a data frame.
env_stat<-readOGR(dsn="SJV/env_stat.sqlite", layer="env_stat")


#this is the tract_comb origin, so where it is referenced, here is how it was created
tract_comb<-as(env_stat, "sf")





cal_urb<-readOGR(dsn="SJV/urban_tracts.sqlite", layer="urban_tracts")

#here is a good example of converting data frame types


cal_urb2<-as(cal_urb,"sf")

cal_urb3<-cal_urb2%>%group_by(tract)%>%summarize(urb_area = sum(acres))

cal_urb4<- as.data.frame(cal_urb3)




cal_ag4<-as.data.frame(agr_sf2)


cal_merged<-cal_ag4%>%full_join(cal_urb4, by=c("tract"))%>%mutate(ag_area = replace(ag_area, is.na(ag_area), 0), urb_area=replace(urb_area, is.na(urb_area),0))

merged2<-cal_merged%>%full_join(env_sf, by=c("tract"))

env_sf2<-merged2%>%full_join(as.data.frame(env_sf), by = c("tract"))



#projecting gaslines
gas_WGS842 <- spTransform(gas_lines,
                                CRS(("+proj=robin +datum=WGS84")))

#NAD 83 projection for gaslines
gas_NAD83 <- spTransform(gas_lines,
                                CRS(("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")))


#more projections etc
tract_WGS84 <- spTransform(tract_cent,
              CRS(("+proj=robin +datum=WGS84")))

trans_WGS84 <- spTransform(trans_lines,
              CRS(("+proj=robin +datum=WGS84")))

gas_WGS84 <- spTransform(gas_lines,
              CRS(("+proj=robin +datum=WGS84")))


tract_NAD83 <- spTransform(tract_cent,
                                CRS(("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")))


ca_roads<-readOGR(dsn="SJV/ca_roads.sqlite", layer="ca_roads")

roads_NAD83 <- spTransform(ca_roads,
                                CRS(("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")))

trans_NAD83 <- spTransform(trans_lines,
                                CRS(("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")))


roads_WGS84 <-spTransform(ca_roads,CRS(("+proj=robin +datum=WGS84")))


#EUCLIDEAN DISTANCE CALCULATIONS

p3 <- gDistance(gas_NAD83,tract_NAD83,  byid=TRUE)

p2 <- gDistance(trans_NAD83,tract_NAD83,  byid=TRUE)

p1 <- gDistance(roads_NAD83,tract_NAD83,  byid=TRUE)

#UPDATING DATASET WITH DISTANCES INCLUDED
tracts<-as.data.frame(tract_cent)%>%mutate(gas_distance = apply(p3, 1, FUN=min)/1000, trans_dist = apply(p2, 1, FUN=min)/1000, road_dist = apply(p1, 1, FUN=min)/1000)

#MAKE NEW COMPLETE DATASET
tract_comb<-as.data.frame(tracts)%>%distinct(id,.keep_all = TRUE)%>%full_join(merged2, by = c("tract"))

write.csv(tracts, file = "SJV/final_file_pre_merge.csv")
write.csv(tracts, file = "SJV/final_file_post_merge.csv")
```





Here are examples of doing these things with just Tulare County

```{r pressure, echo=FALSE}
file.exists('c:/users/Andre/Downloads/Tulare/tulag.sqlite')


env_sf<-readOGR(dsn="c:/users/Andre/Downloads/env.sqlite", layer="env")

env_sf<-env_sf%>%mutate(light_dens = fr_gmean/shape_area)

#Tulare agricultural data
tul_ag<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tulag.sqlite", layer="tulag")

sjv_pt<-readOGR(dsn="c:/users/Andre/Downloads/sjv_pt.sqlite", layer="sjv_pt")

#Tular road data
tul_roads<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tul_roads2.sqlite", layer="tul_roads2")

tul_r<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tul_r.sqlite", layer="tul_r")

tul_env<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tulenv.sqlite", layer="tulenv")

tul_traffic<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tul_traffic.sqlite", layer="tul_traffic")

tul_sjv<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tulsjv2.sqlite", layer="tulsjv2")

tul_swis<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tul_swis2.sqlite", layer="tul_swis2")

ca_roads<-readOGR(dsn="c:/users/Andre/Downloads/ca_roads.sqlite", layer="ca_roads")

tul_st<-readOGR(dsn="c:/users/Andre/Downloads/Tulare/tul_st.sqlite", layer="tul_st")

nightlight<-readOGR(dsn="c:/users/Andre/Downloads/narrow_nighlight.sqlite", layer="narrow_nighlight")

nightlight_csv<-as(nightlight, "sf")

CRS(tul_sjv)
gas_WGS84 <- spTransform(gas_lines,
                                CRS(("+proj=robin +datum=WGS84")))

tul_roads_WGS84 <- spTransform(tul_roads,
                                CRS(("+proj=robin +datum=WGS84")))

tul_sjv_WGS84 <- spTransform(tul_sjv,CRS(("+proj=robin +datum=WGS84")))

sjv_WGS84 <- spTransform(sjv,CRS(("+proj=robin +datum=WGS84")))

ca_roads_WGS84 <- spTransform(ca_roads,CRS(("+proj=robin +datum=WGS84")))

sjv_pt_WGS84 <- spTransform(sjv_pt,CRS(("+proj=robin +datum=WGS84")))

plot(density(nightlight_csv$value))

tul_roads_WGS84 <- spTransform(tul_roads,CRS(("+proj=robin +datum=WGS84")))

tul_swis_WGS84 <- spTransform(tul_swis,CRS(("+proj=robin +datum=WGS84")))

tul_st_WGS84 <- spTransform(tul_st,CRS(("+proj=robin +datum=WGS84")))


```

Here are some plots of just Tulare County based on all the files we imported and manipulated in the previous frame. You can plot geospatial information usng the ggplot package!! It might be easier sometimes to just export files and do the plotting in QGIS, but it's nice to know that there is functionality here as well.
```{r}
tul<-as(tul_sjv_WGS84,'sf')

ggplot(tul_env) + 
  aes(long,lat,group=group) + 
  geom_polygon() +
  geom_path(color="white") +
  geom_point(data = tul, aes(x = longitude, y = latitude),col="red", size=5)
  

ggplot( aes(long,lat,group=group) ,data=tul_env)+geom_polygon()+geom_point(aes(x = longitude, y = latitude),data=tul,col="red", size=5)
  
  #stat_density_2d(aes(longitude, latitude, colour=population, data=tul), geom = "polygon", colour="white")




plot(tul_env, xlim = c(-118, -120), ylim = c(35, 37), asp = 1)+plot(tul_ag)

plot(tul_env, col='light gray', border='gray')
plot(tul_ag, add=TRUE, density=20, lwd=2, col='red')
plot(tul_roads, add=TRUE, density=20, lwd=2, col='red')
plot(tul_traffic, add=TRUE, density=20, lwd=2, col='blue')
plot(tul_sjv, add=TRUE, density=20, lwd=2, col='green')
plot(gDistance(tul_sjv_WGS84, tul_roads_WGS84, byid=TRUE), add=TRUE, density=20, lwd=2, col='green')

d <- density(tul$population)

ggplot() + 
  geom_polygon(aes(long,lat,group=group), data=tul_env, fill="lightsteelblue3", color="dark gray" ) +
  geom_path(aes(long,lat,group=group), color="white", data=tul_env) +
  geom_point(aes(x = longitude, y = latitude, size=population), data = tul, col="black")+
  


gg<-ggplot() + 
  geom_polygon(aes(long,lat,group=group), data=tul_env, color="dark gray" ) +
  geom_path(aes(long,lat,group=group), color="white", data=tul_env)

gg

gg+stat_density2d(data=tul, show.legend=F, aes(x=longitude, y=latitude, fill=..level.., alpha=..level..), geom="polygon", size=2, bins=15)+ scale_fill_gradient(low="gray99", high="firebrick1", name="Distribution")

tul_traf<-as(tul_traffic, "sf")

gg+###stat_density2d(data=tul, show.legend=F, aes(x=longitude, y=latitude,fill = stat(nlevel), fill=..level.., alpha=..level..), geom="polygon", size=2, bins=15)+
  #scale_fill_viridis_c()+
  geom_point(aes(x = longitude, y = latitude, size=ahead.peak.hour), data = tul_traf, col="black", alpha=0.1)+
  geom_point(aes(x = longitude, y = latitude, size=population), data = tul, col="red", alpha=0.1)

tract_comb3<-tract_comb3%>%mutate(pred_pop = fun(light_dens))
```





```{r}

```



Practicing distance calculations using just tulare county. 
```{r}
ca_roads2_WGS84<-as(ca_roads_WGS84, "SpatialLines")

tul_roads2_WGS84<-as(tul_roads_WGS84, "SpatialLines")

tul_sjv2_WGS84<-as(tul_sjv_WGS84, "SpatialPoints")

sjv_pt2_WGS84<-as(sjv_pt_WGS84, "SpatialPoints")

tul_sjv2<-as(tul_sjv_WGS84, "sf")

plot(tul_roads2_WGS84, xlab = "Longitude", ylab = "Latitude", main = "SpatialPoints + SpatialLines")
plot(tul_sjv2_WGS84, add = TRUE, xlab = "Longitude", ylab = "Latitude", main = "SpatialPoints + SpatialLines")

m <- gDistance(tul_sjv2_WGS84, tul_roads2_WGS84, byid=TRUE)

n <- gDistance(tul_sjv2_WGS84, tul_swis_WGS84, byid=TRUE)

## Finds single closest in

tul_sjv2<-tul_sjv2 %>%mutate(road_distance = apply(m, 2, function(X)rownames(m)[order(X)[1]]))

rownames(m)[order(X)][1:10] ## Finds 10 closest
p<-apply(road_dist, 2, function(X)rownames(m)[order(X)[1]])

sjv2<-sjv %>%mutate(road_distance = apply(road_dist, 2, function(X)rownames(n)[order(X)[1]]))

tul_csv<-as(tul_env, "sf")

tul_ag2<-as(tul_ag, "sf")


#FOR ALL OF CA, NOT JUST TULARE.
road_dist<- gDistance(sjv_pt2_WGS84, ca_roads2_WGS84, byid=TRUE)


rownames(road_dist)[order(X)][1:10] ## Finds 10 closest
p<-apply(road_dist, 2, function(X)rownames(road_dist)[order(X)[1]])

sjv2<-as(sjv_pt_WGS84, "sf")

sjv2<-sjv2 %>%mutate(road_distance = apply(road_dist, 2, function(X)rownames(road_dist)[order(X)[1]]))

env6<-as(env3, "Spatial")

ggplot() + 
  geom_polygon(aes(long,lat,group=group), data=env6, fill="lightsteelblue3", color="dark gray" ) +
  geom_path(aes(long,lat,group=group), color="white", data=tul_env) +
  geom_point(aes(x = longitude, y = latitude, size=road_distance), data = tul_sjv2, col="black", alpha=0.1) +
  geom_path(aes(long,lat,group=group), color="red", data=tul_roads)
```





```{r}

ggplot() + 
  geom_polygon(aes(long,lat,group=group), data=tul_env, fill="lightsteelblue3", color="dark gray" ) +
  geom_path(aes(long,lat,group=group), color="white", data=tul_env) +
  geom_point(aes(x = longitude, y = latitude, size=road_distance), data = tul_sjv2, col="black", alpha=0.1) +
  geom_path(aes(long,lat,group=group), color="red", data=tul_roads)
  

gg<-ggplot() + 
  geom_polygon(aes(long,lat,group=group), data=tul_roads,  color="dark gray" ) +
  geom_path(aes(long,lat,group=group), color="white", data=tul_env, )

gg

gg+stat_density2d(data=tul, show.legend=F, aes(x=longitude, y=latitude, fill=..level.., alpha=..level..), geom="polygon", size=2, bins=15)+ scale_fill_gradient(low="gray99", high="firebrick1", name="Distribution")

tul_sjv3<-as(tul_sjv2, "Spatial")
merged<-over( tul_sjv3 , tul_env , fn = NULL) 


```





